---
title: "Welcome to Dr Simon Thornley's digital droplet"
author: ""
date: "`r format(Sys.time(), '%e %B, %Y')`"
output: html_document
prettydoc::html_pretty:
      theme: tactile
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(vembedr)
```


## Thanks for visiting!

This is my shiny server, where I host a bunch of web apps.

## POPLHLTH 304

I teach in the University of Auckland's undergraduate Bachelor of Health Science.

I teach stage 3 university students to learn `R` skills through interactive tutorials.

Some of these tutorials are found on links below:

- [Tutorial 2: Getting started with R.    ](http://sithor.com/shiny/304_tutorials/Tut_2/){target="_blank"}
- [Tutorial 3: Getting started with posit.    ](http://sithor.com/shiny/304_tutorials/Tut_3/){target="_blank"}
- [Tutorial 4: Statistical testing.    ](http://sithor.com/shiny/304_tutorials/Tut_4/){target="_blank"}
- [Tutorial 5: Linear regression.    ](http://sithor.com/shiny/304_tutorials/Tut_5/){target="_blank"}
- [Tutorial 6: Count regression.    ](http://sithor.com/shiny/304_tutorials/Tut_6/){target="_blank"}
- [Tutorial 8: Logistic regression.    ](http://sithor.com/shiny/304_tutorials/Tut_8/){target="_blank"}


## Other epidemiology-related apps and websites

- [Calculate and visualise relative risks and odds ratios](http://sithor.com/shiny/Relative_risk_shiny/){target="_blank"}
- [Analyse food outbreak data](http://sithor.com/shiny/Food_outbreak/){target="_blank"}
- [My epidemiology glossary](https://rpubs.com/sithor/epidemiological_glossary){target="_blank"}
- [Visualise a count regression example](https://rpubs.com/sithor/Permethrin_ARF_regression){target="_blank"}
- [Visualise a logistic regression example](https://sithor.shinyapps.io/Logistic_regression/){target="_blank"}
- [Dice simulation of an epidemiological study](https://sithor.shinyapps.io/Epi_teaching/){target="_blank"}
- [Regression and principal components](https://sithor.shinyapps.io/regress_princomp/){target="_blank"}
- [Bayes' diagnostic test aid](https://sithor.shinyapps.io/Bayes_Diagnostic_test/){target="_blank"}
[Calculator for in-hospital interpretation of D-dimer test](https://sithor.shinyapps.io/Pulmonary_embolus/){target="_blank"}
- [My github page](https://github.com/sithor/){target="_blank"}

## Some of my talks
<br></br>
```{r echo = FALSE}
embed_url("https://www.youtube.com/watch?v=rYq82gh7gZE")
```

<br></br>

```{r echo = FALSE}
embed_url("https://www.youtube.com/watch?v=9FROFwHjEms&t=1545s")
```

<br></br>

```{r echo = FALSE}
embed_url("https://www.youtube.com/watch?v=fqxNUV1aesg")
```

<br></br>

```{r echo = FALSE}
embed_url("https://www.youtube.com/watch?v=7iEe8ZYyrhA")
```

<br></br>

```{r echo = FALSE}
embed_url("https://www.youtube.com/watch?v=GwmJDhOyp2c")
```

My [interview](https://www.1news.co.nz/2020/09/06/not-lockdowns-controversial-epidemiologist-calls-for-end-to-irrational-covid-19-elimination-strategy/){target="_blank"} with Jack Tame on Q&A on aired on TVNZ (September 6, 2020).